Epidemiological Data Analysis

### 2023-11-06 analysis/epi_analysis.Rmd
minor fix

# number of cases by week
cases_by_cond_pl <- epi_data %>%
  group_by(aircleaner) %>%
  summarize(cases = sum(new_cases)) %>%
  ungroup() %>%
  mutate(aircleaner = factor(aircleaner, levels = c("No", "Yes"))) %>%
  ggplot(aes(x = aircleaner, y = cases, fill = aircleaner)) +
  geom_bar(stat = "identity", color = "black", width = .4) +
  geom_text(mapping = aes(label = cases), size = 8 / cm(1), vjust = -1) +
  ggsignif::geom_signif(annotations = "Posterior prob. = 91%", y_position = 27, xmin = 1, xmax = 2, 
                        textsize = 8 / cm(1), vjust = -.5, tip_length = .075) +
  labs(x = "Air cleaner", y = "Number of respiratory cases", fill = "Air cleaner", title = "a") +
  scale_fill_manual(values = bluegrey) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), breaks = scales::pretty_breaks(4)) +
  theme_custom() +
  theme(plot.title.position = "plot") +
  guides(fill = "none")

>>>>

# number of cases by week
cases_by_cond_pl <- epi_data %>%
  group_by(aircleaner) %>%
  summarize(cases = sum(new_cases)) %>%
  ungroup() %>%
  mutate(aircleaner = factor(aircleaner, levels = c("No", "Yes"))) %>%
  ggplot(aes(x = aircleaner, y = cases, fill = aircleaner)) +
  geom_bar(stat = "identity", color = "black", width = .4) +
  geom_text(mapping = aes(label = cases), size = 8 / cm(1), vjust = -1) +
  ggsignif::geom_signif(annotations = "Posterior prob. = 91%", y_position = 27, xmin = 1, xmax = 2, 
                        textsize = 8 / cm(1), vjust = -.5, tip_length = .075) +
  labs(x = "Air cleaner", y = "Number of respiratory cases", fill = "Air cleaner", title = "b") +
  scale_fill_manual(values = bluegrey) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), breaks = scales::pretty_breaks(4)) +
  theme_custom() +
  theme(plot.title.position = "plot") +
  guides(fill = "none")
